\chapter[The Heritability of Human Connectomes]{The Heritability of Human Connectomes: a Causal Modeling Analysis} \label{chap:heritability}

This chapter documents our investigations into the heritability of structural connectomes in humans. %Importantly, this study approached the heritability problem from a causal perspective and leveraged statistical network models 
This chapter is currently in review at Imaging Neuroscience, and a preprint is available at bioRxiv (DOI: \url{https://doi.org/10.1101/2023.04.02.532875}) and is distributed under the terms of a Creative Commons Attribution License that permits unrestricted use and redistribution provided that the original author and source are credited.

\begin{singlespace}         % you can also use onehalfspace to relax the spacing
    \fullcite{chung2023heritability} \mybibexclude{chung2023heritability}
\end{singlespace} 

\pagebreak
\section*{Abstract}
The heritability of human connectomes - the maps of brain connectivity - is crucial for understanding the influence of genetic and environmental factors on variability in connectomes and their implications for behavior and disease. Unfortunately, current heritability methods can mistake correlation for causation or use models that oversimplify the intricate nature of brain networks, which risks misinterpreting the influence of genetics on brain connectivity patterns. To address these limitations, we propose a new approach that combines causal inference techniques to control for potential confounding with statistical models designed to capture the complex dependencies within brain networks. This allows us to explore more nuanced concepts of connectome heritability by systematically removing shared network structures. Applying our methods to diffusion connectomes derived from the Human Connectome Project, we show that brain connectivity is heritable heritability, even after adjustments for factors like neuroanatomy, age, and sex. However, once we address for common network between connectomes, our causal tests are no longer significant. These results suggest that previous conclusions on connectome heritability may be driven by the shared network structures. Thus, this work highlights the importance for future works to continue to develop data-driven heritability models which faithfully reflect potential confounders and network structures.
\pagebreak


\input{herit/2.introduction}
\input{herit/3.results}
\input{herit/4.discussion}
\input{herit/5.methods}
\input{herit/6.endnotes}
\input{herit/7.appendix}