\chapter{Statistical Models and Algorithms for Networks} \label{chap:statistical}

This chapter provides a comprehensive introduction to statistical models, assumptions, algorithms and their applications to network and connectomic analyses. We hope this overview will spur further development of statistically grounded methods in connectomics. This chapter was originally published in Annual Review of Statistics and Its Application in March 2021 (DOI: \url{https://doi.org/10.1146/annurev-statistics-042720-023234}) and is distributed under the terms of a Creative Commons Attribution License that permits unrestricted use and redistribution provided that the original author and source are credited.

\begin{singlespace}         % you can also use onehalfspace to relax the spacing
    \fullcite{chung2021statistical} 
\end{singlespace} 

\pagebreak
\section*{Abstract}
The data science of networks is a rapidly developing field with myriad applications.  In neuroscience, the brain is commonly modeled as a connectome, a network of nodes connected by edges. While there have been thousands of papers on connectomics, the statistics of networks remains limited and poorly understood.  Here, we provide an overview from the perspective of statistical network science of the kinds of models, assumptions, problems, and applications that are theoretically and empirically justified for analysis of connectome data.  We hope this review spurs further development and application of statistically grounded methods in connectomics.
\pagebreak

\input{dnd/1.Introduction}
\input{dnd/2.Representations}
\input{dnd/3.Models}
\input{dnd/4.Algorithms}
\input{dnd/5.Theory}
\input{dnd/6.Data}
\input{dnd/6.SingleGraphs}
\input{dnd/7.MultipleGraphs}
\input{dnd/8.Discussion}
\input{dnd/9.Appendix}